First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-03-31 ms.tex
Apparently I didnt save all the line breaks earlier.

The remainder of this paper is organized as follows. In Section~\ref{sec:MWA} we briefly describe the MWA instrument and the observations used in this work, in Section~\ref{sec:analysis} we describe our analysis pipeline, in Section~\ref{sec:techniques} we describe several novel techniques in our analysis, in Section~\ref{sec:deep} we discuss our efforts to apply the analysis pipeline to a deep data integration, and we discuss future work in Section~\ref{sec:discussion}. Throughout this paper we use a $\Lambda$CDM cosmology with $\Omega_m=0.73$, $\Omega_\Lambda=0.27$, and $h = 0.7$, consistent with WMAP seven year results \citep{Komatsu:2011}. All distances and wavenumbers are in comoving coordinates.

@@

\section{Analysis Pipeline}\label{sec:analysis}
In order to ensure consistency in analysis, the international MWA EoR collaboration has defined two independent reference analysis pipelines. The details of this strategy are outlined in D.~C.~Jacobs et al. 2016 (in review). This study is based on the FHD-to-\eppsilon pipe, which is in turn based on the Fast Holographic Deconvolution (FHD\footnote{\url{https://github.com/miguelfmorales/FHD}}, \citealt{Sullivan:2012}) and Error Propagated Power Spectrum with Interleaved Observed Noise (\eppsilon\footnote{\url{https://github.com/miguelfmorales/eppsilon}}, B.~J.~Hazelton et al. 2016, in prep) packages. The general flow of the pipeline is shown in Figure~\ref{fig:pipe}, and we give an overview below.

@@

\subsection{Preprocessing}\label{subsec:preprocessing}
The preprocessing step converts the data from the non-standard memory dump format from the correlator's GPUs to a standard UVFITS format \citep{Greisen:2012}, performs flagging, averages in time and freqeuncy, and writes to disk. For this step we use the \cotter package, which in turn calls the \texttt{AOFLAGGER}\footnote{\url{http://aoflagger.sourceforge.net/}} to perform RFI flagging \citep{Offringa:2010}.

@@

In the first calibration step we allow our complex gains to account for any direction-independent response on a per antenna, per frequency channel, per polarization basis. To define our gains in this way, we have made two simplifications. First we push all direction-dependence of the antenna response into the model of the primary beam. FHD is capable of using separate models for each antenna, though this has not yet been implemented for the MWA due to lack of individual models. The second simplification is to ignore any cross terms between our different axes, for example a mutual coupling between two antennas. In principle these terms would introduce baseline dependent gains, rather than antenna dependent. The MWA has not yet seen evidence of these terms, and so we currently neglect them in our solutions.

>>>>

The remainder of this paper is organized as follows. In Section~\ref{sec:MWA} we briefly 
describe the MWA instrument and the observations used in this work, in Section~
\ref{sec:analysis} we describe our analysis pipeline, in Section~\ref{sec:techniques} we 
describe several novel techniques in our analysis, in Section~\ref{sec:deep} we discuss our 
efforts to apply the analysis pipeline to a deep data integration, and we discuss future work 
in Section~\ref{sec:discussion}. Throughout this paper we use a $\Lambda$CDM 
cosmology with $\Omega_m=0.73$, $\Omega_\Lambda=0.27$, and $h = 0.7$, consistent 
with WMAP seven year results \citep{Komatsu:2011}. All distances and wavenumbers are in 
comoving coordinates.

@@

\section{Analysis Pipeline}\label{sec:analysis}
In order to ensure consistency in analysis, the international MWA EoR collaboration has 
defined two independent reference analysis pipelines. The details of this strategy are 
outlined in D.~C.~Jacobs et al. 2016 (in review). This study is based on the FHD-to-
\eppsilon pipe, which is in turn based on the Fast Holographic Deconvolution (FHD
\footnote{\url{https://github.com/miguelfmorales/FHD}}, \citealt{Sullivan:2012}) and Error 
Propagated Power Spectrum with Interleaved Observed Noise (\eppsilon
\footnote{\url{https://github.com/miguelfmorales/eppsilon}}, B.~J.~Hazelton et al. 2016, in 
prep) packages. The general flow of the pipeline is shown in Figure~\ref{fig:pipe}, and we 
give an overview below.

@@

\subsection{Preprocessing}\label{subsec:preprocessing}
The preprocessing step converts the data from the non-standard memory dump format 
from the correlator's GPUs to a standard UVFITS format \citep{Greisen:2012}, performs 
flagging, averages in time and freqeuncy, and writes to disk. For this step we use the 
\cotter package, which in turn calls the \texttt{AOFLAGGER}\footnote{\url{http://
aoflagger.sourceforge.net/}} to perform RFI flagging \citep{Offringa:2010}.

@@

In the first calibration step we allow our complex gains to account for any direction-
independent response on a per antenna, per frequency channel, per polarization basis. To 
define our gains in this way, we have made two simplifications. First we push all direction-
dependence of the antenna response into the model of the primary beam. FHD is capable 
of using separate models for each antenna, though this has not yet been implemented for 
the MWA due to lack of individual models. The second simplification is to ignore any cross 
terms between our different axes, for example a mutual coupling between two antennas. In 
principle these terms would introduce baseline dependent gains, rather than antenna 
dependent. The MWA has not yet seen evidence of these terms, and so we currently 
neglect them in our solutions.
